---
title: "R Notebook"
output: html_notebook
---


The utilized  input files are a result of local ancetry inference, The results were spllited on the inference made per individual, per chromosome (each file is equal to one haplotype)


#packages loading
``` {r, echo=FALSE, results = FALSE, eval=FALSE}
library(tidyverse)
library(ggplot2)
library(cowplot)
library(data.table)
library(xml2)
library(plyr)
library(dplyr)
library(ggbeeswarm)
library(reshape2)


### deafult changes for calean background and bigger text size

nice_layout<-   theme_cowplot(font_size = 22)+
    panel_border(color = "grey85", size = 1, linetype = 1,
  remove = FALSE, "black") +
    theme(strip.background = element_rect(fill = "#ffffff"), text = element_text(size = 22))


my_cols <- c('#a6cee3','#1f78b4','#b2df8a','#33a02c','#fb9a99','#e31a1c','#fdbf6f','#ff7f00','#cab2d6','#6a3d9a')


stackbarcolors<- c("ambiguous"="#808080", "caudatus"="#a6cee3", "cruentus"="#1f78b4", "hypochondriacus"="#b2df8a", "hybridus_CA"="#33a02c", "hybridus_SA"="#f8bf68", "quitensis"="#fb9a99")
```



# Loading and summarising haplotypes by the classifcation of the donated portion on each position (vertical summary)


```{r}
classfication_summary=list()  # creates a empty list that will be appended as the funtion is applied
column_names<-c("pos", "caudatus", "cruentus", "hypochondriacus", "hybridus_CA", "hybridus_SA", "quitensis")
especies<- c( "caudatus", "cruentus", "hypochondriacus", "hybridus_CA", "hybridus_SA", "quitensis")
especies<-"caudatus"

for (chromosome in 16:16){  #cycles through each chromossome
for (species in especies){ #cycles per spcecies
for (i in 3:3) { #cicles per file == number of pop
      # ... make some data
  name_file <-paste0("/Volumes/T7/hap_data/sc",chromosome,"_haplotypes_",species,i)
    if(file.exists(name_file)) # checks file existance without breaking code in case of missing 
      dados<-fread(name_file)
    dados = dados[-1,]
    colnames(dados) <-column_names #subsitute first row for calculated columns
    dados.transformed<- dados %>%
      dplyr::mutate(donor=case_when( # checks if more than 50% of a site has a certain background
  cruentus > 0.5 ~ "cruentus",
    hypochondriacus > 0.5 ~ "hypochondriacus",
      caudatus > 0.5 ~ "caudatus",
      hybridus_CA > 0.5 ~ "hybridus_CA",
    hybridus_SA > 0.5 ~ "hybridus_SA",
    quitensis > 0.5 ~ "quitensis",
  TRUE   ~ "ambiguous" # when proability is over 1/2 (0.5)
)) %>%
  dplyr::group_by(donor) %>%  # groups by classified donors
  dplyr::summarise(contagem= n() /nrow(.))  #cpounts how many
                dados.transformed$recipient <-paste0(species)  #track of species of recipient 
       dados.transformed$file <-paste0(species,i)  #track of species of recipient and iteration number 
              dados.transformed$chr <-paste0(chromosome)  #track of species of recipient and iteration number 

      classfication_summary<- rbind(classfication_summary,dados.transformed)                   # Append new dataframe as the code iterates each haplotype (one chromossome per inidividual per population at a time)
}
}
}

```

## plot the summary of the vertically classified donors (boxplot) 

```{r}

extneded_classfication_summary<-
melt(classfication_summary, id.vars=c("recipient","donor"))


plot_side_by_side_boxplot<- extneded_classfication_summary %>%
  filter(variable=='contagem') %>%
  ggplot(aes(x=factor(recipient), y=as.numeric(value), fill=factor(donor))) +
  geom_boxplot(outlier.shape = NA) +
        ylim(0,1) +
    labs(fill='donor') +
  xlab("recipient") +
  ylab("proportion") +
  nice_layout +
  scale_fill_manual(values = stackbarcolors) +
        scale_color_manual(values = stackbarcolors) +  
    facet_grid(.~recipient, scales = "free") +
  # theme(strip.text.x = element_text(angle = 45, size =13)) +
                # theme(axis.text.x = element_blank())  
  theme(strip.text.x = element_blank()) +
  theme(axis.text.x=element_text(size=18)) +
theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
  labs(title = "Proportion distribution per population (chr 16)")

plot_side_by_side_boxplot
# 
# ggsave( "../data/processed/figures/plot_side_by_side_boxplot_sc16.pdf", plot_side_by_side_boxplot, device="pdf", width = 12, height =8)

```



## preparation of haplotype analysis along the genome (horizontal summary)

```{r}

classification_along=list()
column_names<-c("pos", "caudatus", "cruentus", "hypochondriacus", "hybridus_CA", "hybridus_SA", "quitensis")
# especies<- c("cau", "cru", "hyp", "hyb", "qui")
# especies<- c( "caudatus", "cruentus", "hypochondriacus", "hybridus_CA", "hybridus_SA", "quitensis")
especies<-"cruentus"
subsample_chr_list<-(c(3:3)) #ubsample due to exhausted vector

for (chromosome in subsample_chr_list){
for (species in especies){
for (i in 5:5) {
  name_file <-paste0("/Volumes/T7/hap_data/sc",chromosome,"_haplotypes_",species,i)
    if(file.exists(name_file)) {
      dat<-fread(name_file)
    dat = dat[-1,]
    colnames(dat) <-column_names #subsitute first row for calcualted columns
    dat.transformed<- dat %>%
      dplyr::mutate(donor=case_when(
  cruentus > 0.5 ~ "cruentus",
    hypochondriacus > 0.5 ~ "hypochondriacus",
      caudatus > 0.5 ~ "caudatus",
      hybridus_CA > 0.5 ~ "hybridus_CA",
    hybridus_SA > 0.5 ~ "hybridus_SA",
    quitensis > 0.5 ~ "quitensis",
  TRUE   ~ "ambiguous" # when proability is over 1/2 (0.5)
)) 
        dat.transformed$recipient <-paste0(species)  #track of species of recipient 
        dat.transformed$file <-paste0(species,i)  #track of species of recipient and iteration number 
       dat.transformed$chr <-paste0(chromosome)  #track of species of recipient and iteration number 

      classification_along<- rbind(classification_along,dat.transformed)   
      # Append new dataframe
    }
else {print(paste0("The file does not exist, so it was skipped", name_file))
}
  }
}
}

options(scipen=999)

```


## plot haplotypes along the genome (individuals files)
### Stackbar plots

```{r}
ggsave("../data/processed/figures/caudatus_3_along_the genome_chromosome_9.png",
listagem%>%
  ggplot(.,aes(x=donor, y=contagem, fill=donor)) +
  geom_bar(stat="identity") +
   facet_grid(.~chr, scales="free") +
  nice_layout +
      theme(axis.text.x = element_blank(),
            axis.ticks = element_blank()) +
        scale_fill_manual(values = stackbarcolors) +
        scale_color_manual(values = stackbarcolors) +  
  ggtitle("caudatus3 PI490612 "), 
height = 8, width =18)
```

## lineplot (smooth without self)

```{r}
 ggsave("/Users/josedias/Desktop/cruentus_5_smooth_chromosome_sc3.png",

lista %>%
  # filter(pos<1000000) %>%
  ggplot() +
  geom_smooth( aes(x = as.numeric(pos), y=quitensis, color="quitensis")) +
    geom_smooth(aes(x = pos, y=cruentus, color="cruentus")) +
      geom_smooth(aes(x = pos, y=caudatus, color="caudatus")) +
        geom_smooth(aes(x = pos, y=hybridus_CA, color="hybridus_CA")) +
        geom_smooth(aes(x = pos, y=hybridus_SA, color="hybridus_SA")) +
  nice_layout +
          scale_color_manual(values = stackbarcolors) +  
  theme(legend.position = "bottom") ,
height = 8, width =18)

```




